---
title: "Profiling plots 2021"
author: "Emanuel Mauch"
date: "2023-08-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The following plots are Thermoclines from the ponds used for the Stickleback-
experiments in 2021.
This profiles are used to estimate the actively mixed layer depth of the ponds, which
are subsequently used to model metabolism (GPP, R, NEP).

# Pond-profiles
## B1P1

This is the code for B1P1, the other ponds were analysed equivalently:
```{r, message=FALSE}
# Step 0: set up R-script ------------------------------------------------------
rm(list= ls())

setwd("~/ZIVI_EAWAG/project_21")

source("~/ZIVI_EAWAG/project_21/Moritz_Luehrig_paper_stuff/methods_packages.R")
library(GGally)

# Profile B1P1 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B1P1Sept10_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]

# Rename columns
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 762:812, where the profiling was done
prof <- prof[c(762:812),]

# Create the thermocline plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B1P1 2021-09-10")
```
I interpret that the mixed layer depth in B1P1 was at least 3.163m on Sept 10 2021,
since the demperature differences from top to bottom are only minimal (< 0.5°C).

## B2P2
```{r, echo=FALSE, warning=FALSE}
# Profile B2P2 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P2_Sept12_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 936-964, where the profiling was done
prof <- prof[c(936:964),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P2 2021-09-12")
```
I interpret that the mixed layer depth in B2P2 was at least 1.916m on Sept 12 2021,
since the demperature differences from top to bottom are only minimal (< 0.1°C)


## B3P3
```{r, echo=FALSE, warning=FALSE}
# Profile B3P3 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P3_Sept13_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 811:856, where the profiling was done
prof <- prof[c(811:856),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P3 2021-09-13")
```
I interpret that the mixed layer depth in B3P3 was at least 3.933m on Sept 13 2021,
since the temperature differences from top to bottom are only minimal (< 0.2°C)

## B2P3
```{r, echo=FALSE, warning=FALSE}
# Profile B2P3 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P3_Sept12_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 588:619, where the profiling was done
prof <- prof[c(588:619),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P3 2021-09-12")
```
I interpret that the mixed layer depth in B2P3 was at least 2.842 on Sept 12 2021,
since the temperature differences from top to bottom are only minimal (< 0.1°C)

# B3P1
```{r, echo=FALSE, warning=FALSE}
# Profile B3P1 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P1_Sept13_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 943:966, where the profiling was done
prof <- prof[c(943:966),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P1 2021-09-13")
```
I interpret that the mixed layer depth in B3P1 was at least 1.494m on Sept 13 2021,
since the temperature differences from top to bottom are only minimal (< 0.2°C).

# B3P2
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P2_Sept13_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 979:1028, where the profiling was done
prof <- prof[c(979:1028),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P2 2021-09-13")
```
I interpret that the mixed layer depth in B3P2 was at least 2.988m on Sept 13 2021,
since the temperature differences from top to bottom are only minimal (< 0.1°C).

## B3P0
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P0_Sept13_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 649:694, where the profiling was done
prof <- prof[c(649:694),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P0 2021-09-13")
```
I interpret that the mixed layer depth in B3P0 was at least 2.978m on Sept 13 2021,
since the temperature differences from top to bottom are only minimal (< 0.1°C).

## ERL85
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL85_Sept21_2021.csv", sep = ",")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 991:1108, where the profiling was done
prof <- prof[c(992:1108),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL85 2021-09-21")
```
I interpret that the mixed layer depth in ERL85 was at least 6.819m on Sept 21 2021,
since the temperature differences from top to bottom are only minor (< 0.6°C).

## B2P4
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P4_Sept15_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 912:969, where the profiling was done
prof <- prof[c(912:969),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P4 2021-09-15")
```
Even though the temperature difference from top to bottom is about 1.4°C,
I would say that the mixed layer depth of B2P4 on Sept 15 2021 was at least
4.857m.

## ERL152
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL152_Sept16_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 521:565, where the profiling was done
prof <- prof[c(521:565),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL152 2021-09-16")
```
I interpret that the mixed layer depth in ERL152 was at least 4.117m on Sept 16 2021,
since the temperature differences from top to bottom are only minor (< 0.2°C)

## ERL122
```{r, echo=FALSE, warning=FALSE}
# Profile ERL122 ---------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL122_Sept16_2021.csv", sep = ";")
# In lake ERL122, the profile datset seems to be cut right about at the moment the sondes
# reaches its deepest point

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 515:561, where the profiling was done
prof <- prof[c(515:561),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL122 2021-09-16")
```
I interpret that the mixed layer depth in ERL122 was at least 3.783m on Sept 16 2021,
since the temperature differences from top to bottom are only minor (< 0.4°C)

## B1P4 
```{r, echo=FALSE, warning=FALSE}
# Profile B1P4 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B1P4_Sept11_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 1148:1193, where the profiling was done
prof <- prof[c(1148:1193),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B1P4 2021-09-11")
```
I interpret that the mixed layer depth in B1P4 was at least 1.681m on Sept 11 2021,
since the temperature differences from top to bottom are only minimal (< 0.1°C).

# Appendix
## Version and packages used to generate this report:
```{r, echo=FALSE}
cat(paste(Sys.time(), Sys.timezone(), "\n"))
sessionInfo()
```

## Code used to generate the plots:
```{r, eval=FALSE}
################################################################################
# This is a code to plot the sondes profiles of 2021 to determine a reasonable
# actively mixed layer depth for the metabolism models of the different ponds
################################################################################

# Step 0: set up R-script ------------------------------------------------------
rm(list= ls())

setwd("~/ZIVI_EAWAG/project_21")

source("~/ZIVI_EAWAG/project_21/Moritz_Luehrig_paper_stuff/methods_packages.R")
library(GGally)

# Profile B1P1 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B1P1Sept10_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]

# Rename columns
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 762:812, where the profiling was done
prof <- prof[c(762:812),]

# Create the thermocline plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B1P1 2021-09-10")

# I interpret that the mixed layer depth in B1P1 was at least 3.163m on Sept 10 2021,
# since the demperature differences from top to bottom are only minimal (< 0.5°C)


# Profile B2P2 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P2_Sept12_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 936-964, where the profiling was done
prof <- prof[c(936:964),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P2 2021-09-12")

# I interpret that the mixed layer depth in B2P2 was at least 1.916m on Sept 12 2021,
# since the demperature differences from top to bottom are only minimal (< 0.1°C)

# Profile B3P3 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P3_Sept13_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 811:856, where the profiling was done
prof <- prof[c(811:856),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P3 2021-09-13")

# I interpret that the mixed layer depth in B3P3 was at least 3.933m on Sept 13 2021,
# since the temperature differences from top to bottom are only minimal (< 0.2°C)

# Profile B2P3 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P3_Sept12_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 588:619, where the profiling was done
prof <- prof[c(588:619),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P3 2021-09-12")

# I interpret that the mixed layer depth in B2P3 was at least 2.842 on Sept 12 2021,
# since the temperature differences from top to bottom are only minimal (< 0.1°C)

# Profile B3P1 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P1_Sept13_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 943:966, where the profiling was done
prof <- prof[c(943:966),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P1 2021-09-13")

# I interpret that the mixed layer depth in B3P1 was at least 1.494m on Sept 13 2021,
# since the temperature differences from top to bottom are only minimal (< 0.2°C)

# Profile B3P2 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P2_Sept13_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 979:1028, where the profiling was done
prof <- prof[c(979:1028),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P2 2021-09-13")

# I interpret that the mixed layer depth in B3P2 was at least 2.988m on Sept 13 2021,
# since the temperature differences from top to bottom are only minimal (< 0.1°C)

# Profile B3P0 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P0_Sept13_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 649:694, where the profiling was done
prof <- prof[c(649:694),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P0 2021-09-13")

# I interpret that the mixed layer depth in B3P0 was at least 2.978m on Sept 13 2021,
# since the temperature differences from top to bottom are only minimal (< 0.1°C)

# Profile ERL85 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL85_Sept21_2021.csv", sep = ",")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 991:1108, where the profiling was done
prof <- prof[c(992:1108),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL85 2021-09-21")

# I interpret that the mixed layer depth in ERL85 was at least 6.819m on Sept 21 2021,
# since the temperature differences from top to bottom are only minor (< 0.6°C)

# Profile B2P4 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P4_Sept15_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 912:969, where the profiling was done
prof <- prof[c(912:969),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P4 2021-09-15")

# Even though the temperature difference from top to bottom is about 1.4°C,
# I would say that the mixed layer depth of B2P4 on Sept 15 2021 was at least
# 4.857m.

# Profile ERL152 ---------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL152_Sept16_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 521:565, where the profiling was done
prof <- prof[c(521:565),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL152 2021-09-16")
# I interpret that the mixed layer depth in ERL152 was at least 4.117m on Sept 16 2021,
# since the temperature differences from top to bottom are only minor (< 0.2°C)

# Profile ERL122 ---------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL122_Sept16_2021.csv", sep = ";")
# In lake ERL122, the profile datset seems to be cut right about at the moment the sondes
# reaches its deepest point

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 515:561, where the profiling was done
prof <- prof[c(515:561),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL122 2021-09-16")
# I interpret that the mixed layer depth in ERL122 was at least 3.783m on Sept 16 2021,
# since the temperature differences from top to bottom are only minor (< 0.4°C)

# Profile B1P4 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B1P4_Sept11_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 1148:1193, where the profiling was done
prof <- prof[c(1148:1193),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B1P4 2021-09-11")
# I interpret that the mixed layer depth in B1P4 was at least 1.681m on Sept 11 2021,
# since the temperature differences from top to bottom are only minimal (< 0.1°C)
```

